### 2022-03-18 CV/cv-sections/papers.tex
-

\cventry
{Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtárik} % Authors
{IntSGD: Floatless Compression of Stochastic Gradients} % Title
{\href{https://openreview.net/forum?id=pFyXqxChZc}{ICLR 2022}}
{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}} 
{16 Feb 2021} % Date
{}

>>>>

\cventry
{Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtárik} % Authors
{IntSGD: Floatless Compression of Stochastic Gradients} % Title
{\href{https://openreview.net/forum?id=pFyXqxChZc}{ICLR 2022}}
%{\href{https://arxiv.org/abs/2102.08374}{arXiv 2021}}
{16 Feb 2021} % Date
{}
